---
title: "API Example: Loan Approval Using R"
author: "Tomy Tjandra"
output: rmdformats::readthedown
---

# Single Prediction

Load library for HTTP Request:

```{r}
library(httr)
```

Prepare single data in a list:

```{r}
single_data <- list(
  Gender = 'Male',
  Married = 'No',
  Dependents = '0',
  Education = 'Graduate',
  Self_Employed = 'No',
  ApplicantIncome = 10000,
  CoapplicantIncome = 10000,
  LoanAmount = 1000,
  Loan_Amount_Term = 30,
  Credit_History = 1.0,
  Property_Area = 'Urban'
)
```

Make a POST Request to the API endpoint in json format:

```{r}
r <- POST(url = 'https://loan-approval-app.herokuapp.com/result',
          body = single_data,
          encode = 'json')
r
```

See the content of the output:

```{r}
content(r)
```

# Multiple Prediction

Prepare input data, we are using 5 rows only:

```{r}
test_data <- read.csv('https://raw.githubusercontent.com/dphi-official/Datasets/master/Loan_Data/loan_test.csv')
input_data <- head(test_data, 5)
knitr::kable(input_data)
```

Data reshaping from dataframe to multiple lists:

```{r}
library(purrr)

input_list <- purrr::transpose(input_data)
input_list
```

Loop through the list to make multiple POST Request (5 times in this case) to the API endpoint in json format:

```{r}
df_result <- data.frame()

for (i in 1:nrow(input_data)){
  r <- POST(url = 'https://loan-approval-app.herokuapp.com/result',
            body = input_list[[i]],
            encode = 'json')
  
  single_result <- data.frame(
    Loan_ID = input_list[[i]]$Loan_ID,
    Probability = content(r)[[1]],
    Class = content(r)[[2]]
  )
  
  df_result <- rbind(df_result, single_result)
}
```

Store the result in a dataframe:

```{r}
df_result
```